A new model to predict survival in patients with end-stage liver disease

### 2022-07-19 analysis/article.Rmd
refactor: create png and pdf just for non-html output

```{r knitr_setup_word, eval = !knitr::is_html_output(), include = FALSE}
knitr::opts_chunk$set(dpi = 1200)
```

@@

```{r bootrcv, echo = FALSE, fig.width = 8, fig.height = 6, fig.cap = paste('Calibration of AMELD in comparison to MELD, MELD-Na and MELD-Plus7.\n The points mark the mean predicted survival of', ameldcfg$m, 'patients per interval against their observed mean survival. The error bars correspond to the 95 % confidence interval of the survival estimate.'), dev = c('png', 'pdf'), echo = FALSE}
par(cex = 0.9)
plot(
    bootrcv,
    what = "calibration",
    main = "90-day survival",
    legend = FALSE
)

>>>>

```{r knitr_setup_word, eval = !knitr::is_html_output(), include = FALSE}
knitr::opts_chunk$set(dpi = 1200, dev = c("png", "pdf"))
```

@@

```{r bootrcv, echo = FALSE, fig.width = 8, fig.height = 6, fig.cap = paste('Calibration of AMELD in comparison to MELD, MELD-Na and MELD-Plus7.\n The points mark the mean predicted survival of', ameldcfg$m, 'patients per interval against their observed mean survival. The error bars correspond to the 95 % confidence interval of the survival estimate.'), echo = FALSE}
par(cex = 0.9)
plot(
    bootrcv,
    what = "calibration",
    main = "90-day survival",
    legend = FALSE
)
